A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-05 docs/methods/erosion_methods.tex
NM

\title{Viscous Erosion in Porous Media}

% OTHER TITLE POSSIBILITIES
% A fast and accurate method for viscous erosion in a 2D porous medium

@@

Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{} down to human-scale structures and patterns \cite{}. Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay), as well as biological structures like plaque and biofilms. Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most appropriate regime for groundwater flow and the aforementioned biological examples.

@@

>>>>

\title{A boundary-integral framework to simulate \\ the viscous erosion of a porous medium}

% OTHER TITLE POSSIBILITIES
% Viscous Erosion in Porous Media (change 'in' to 'of'?)
% A fast and accurate method for viscous erosion of a 2D porous medium
% A boundary-integral method for viscous erosion of a porous medium
% A computational framework to simulate the viscous erosion of a porous medium

@@

Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{} down to human-scale structures and patterns \cite{}. Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms. Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most appropriate regime for groundwater flow and the aforementioned biological examples.

@@

% a class of problems (processes) collectively referred to as sculpting with flow.
